The Feasibility of Stylometry as a Service

### 2013-12-08 paper/paper.tex
Updated performance notes

\subsubsection{Low-latency.}
The web service should be near-real-time, i.e. low-latency.  We don't
specify a time requirement but the response should be in the order of
milliseconds to seconds.  A high latency system would not be well
suited for a web service.  An example high latency system could simply
entail sending an encrypted email to a third party who uses Anonymouth
locally and returns the encrypted result.  While this high-latency
system seems trivial, note that a naive implementation will reduce the
user's privacy.  For example, email is very subject to traffic
analysis (CITE) and encrypted email is easy to detect (CITE),
therefore this act alone would raise suspiction.  If this third party
was offering a high-latency anonymiziation service for numerous
people, the network graph would be easy to detect.

@@

The stylometric web service should be interoperability with the modern
web architecture.  Specifically, it should be a service based on
Representational State Transfer (REST)\cite{Fielding2000}.  REST web
services define a framework that is client-server, has a uniform
interface based on HTTP verbs, and supports a layered architecture.
These features are in-line with the goals of a stylometric web
service.  Using a REST service, the client software can be a web
browser, which is nearly ubiqiteious on mobile devices.

@@

The performance of the Stylometry Service

@@

HTML5 Canvas attacks: The etherpad implementation uses the new
'canvas' element introduced in HTML5 extensively. Recently an attack
has been documented
(http://www.contextis.com/files/Browser_timing_Attacks.pdf) whereby
Firefox optimizations in the implementation of the
requestAnimationFrame method have been used by to detect differences
in link coloring across frames (allowing an adversary to determine if
a particular styometry service has been visited, for instance)

@@

\section{Evaluation}

@@

@@

\section{Proposal stuff --- will be removed}

\section*{Approach}\label{sec:approach}

We propose to build a stylometric service around JStylo and
Anonymouth.  However, this project is more than just porting JSAN to
the web.  With a migration to a web service from locally running
software, the anonymity attack vector changes significantly.  We
intend to design and evaluate privacy enhancing techniques for
a stylometric web service.

\subsection{Design}

Our design goal is to increase both the anonymity and availability of
JSAN through this service.  In order to increase the anonymity, we
will need to protect the service from traffic analysis, which we
intend to do by running a Tor hidden service.  To improve the
anonymity and effectiveness of JSAN, we intend to incorporate a
third-party re-writer and in the future, a document mixer.  The
document mixer will randomize the target document, potentially with
other target documents, and present a re-writer the mixed document.
The re-writer will be able to use the Anonymouth-like interface to
anonymize the document without being able to infer the author.  Also,
the mixing will help obfuscate the contents of the document as well.
However, for this initial attempt, we will focus on the third-party
anonymization service.

Although in this initial effort we do not intent to conduct usability
testing, we will consider incentive options for re-writers.  Like
other anonymity networks, we believe that anonymity is improved with a
diverse user base.  The challenge is building the user base.  While we
do not intend to conduct user testing for this initial effort, we will
consider various incentive options like actual payment to
gamification.

\subsection{Implementation}

Our initial idea is to host this service on Amazon Web Services
(AWS).  For the user interface, we are planning to implement the front
end in AngularJS.  Since the existing code is Java, migrating to the
Play Framework seems like a natural progression.  The text editor
functionality will be converted to Firepad, an open source
collaborative editor.  While real-time collaboration is not
necessarily needed, we think that an ``Anonymouth'' user, an
Artificial Agent, would assist the re-writer in edits.

@@

\subsection{Novelty}\label{sec:novelty}

There are two significant contributions as a result of this work.  The
first is a stylometric web service.  This will advance the usability
and capabilities of JSAN and provide a framework for more expansive
user testing in the future.  The second contribution is that this is
the first framework for multi-author adversarial stylometry.  While
single author stylometry has been recently studied, multi-author
documents have not received significant attention.

\section*{Evaluation}\label{sec:evaluation}
This effort is intended to produce several artifacts.  The first is an
evaluation of the privacy architecture of a cloud web service.  Here
we intend to describe the challenges and present and evaluate a
privacy-by-architecture system.  Second, we will provide a survey on
various incentive approaches and suggest a possible method.  Lastly,
we will provide a prototype web service and evaluate it.  Specifically
we will compare the web service to the standalone tools and evaluate
it for accuracy and usability.  Additionally, we will experiment with
the third party anonymization by re-writing each other's writing
samples.  We will provide an evaluation on the perceived difficultly
of re-writing one's own work to that in the mixed system.

\section*{Milestones}\label{sec:milestones}

Table \ref{tab:milestones} contains a proposed timeline for completing
this project.  This work will be split among two developers and there
are several modules that can be independently developed.  In order to
re-architect JSAN, we first need to become familiar with the existing
software.  While this software will be running as a service, we do not
intend to release it to the general public in this time-frame.  We
will conduct the evaluation with perhaps a very limited subset of
other students.

>>>>

\subsubsection{Low-latency.}
The web service as implemented is near-real-time, i.e. low-latency,
bounded primarily be the performance of Anonymouth. One key feature of
the current implementation is the asynchronous processing of
stylometric information, which allows a user to continually modify a
text while anonymity information is calculated in the background. The
latency of the response times for each stylometric analysis is on the
order of 1 to 2 minutes in the default configuration (see Performance
section for futher details).

A high latency system would not be well
suited for a web service.  An example high latency system could simply
entail sending an encrypted email to a third party who uses Anonymouth
locally and returns the encrypted result.  While this high-latency
system seems trivial, note that a naive implementation will reduce the
user's privacy.  For example, email is very subject to traffic
analysis (CITE) and encrypted email is easy to detect (CITE),
therefore this act alone would raise suspiction.  If this third party
was offering a high-latency anonymiziation service for numerous
people, the network graph would be easy to detect.

@@

The stylometric web service we implemented is interoperable with the modern
web architecture.  Specifically, it should be a service based on
Representational State Transfer (REST)\cite{Fielding2000}.  REST web
services define a framework that is client-server, has a uniform
interface based on HTTP verbs, and supports a layered architecture.
These features are in-line with the goals of a stylometric web
service.  Using a REST service, the client software can be a web
browser, which is nearly ubiqiteious on mobile devices.

@@

The performance of the Stylometry Service as implemented is largely
determined by that of the Anonymouth service that it uses to get
stylometry suggestions. For an analysis of 1 500-word test document vs
23 documents from 4 'other' authors and using 8 training documents
from the to-anonymize author, we recorded a total of 67 seconds
required for the Anonymouth analysis, with less than 1 additional
second used to update the client UI, on a 3.3 Ghz Core i5 Ubuntu 12.04
Desktop machine, using 1 calculation thread for Anonymouth. These results suggests that any attempts at
performance optimization should center around optimizing the
performance of the Anonymouth configuration.

After each stylometric analysis is complete, the web service ensures
all relevant anonymouth resources are closed. This allows the web
service to be used over a long period of time (20 or more
anonymization attempts have been tested) without memory leaks noted.

Further performance testing and optimization is required in order to support a true
multi-user service. The authors would suggest using a web service
based load test framework, such as Apache's JMeter or LoadUI, in order
to fully test the service under various potential user loads.

@@

HTML5 Canvas attacks: The etherpad implementation uses the new
'canvas' element introduced in HTML5 extensively. Recently an attack
has been documented (see Contextis Browser Timing Attacks white paper) whereby
Firefox optimizations in the implementation of the
requestAnimationFrame method have been used by to detect differences
in link coloring across frames (allowing an adversary to determine if
a particular styometry service has been visited, for instance)

@@

\section{Single User Evaluation}

@@

\section{Multiple Concurrent User Evaluation}

TODO

@@

There are two significant contributions as a result of this work.  The
first is a stylometric web service.  This advances the usability
and capabilities of JSAN and provide a framework for more expansive
user testing in the future. The user testing results suggest that a
web interface may offer usability advantages while still providing a
meaningful increase in author anonymity.  The second contribution is that this is
the first framework for multi-author adversarial stylometry.  Our
results here suggest TODO.

@@
